\section*{Oskar Ingemarsson}
I have been trying get involved in as much as possible in the project.
Very much have been done together in the group. This have been working
splendid and I think that this working style have benefited the project most
greatly. Since every one have touched almost everything the credit should go to
the group. I will however try to write something about what especially I have
done in the project.
\\\\
%I mainly been involved in the processing the raw data from Amazon and work
%concerning the implementation of perceptron. When it comes to the report I
%mainly been writing the problem description, representing text, feature vectors
%and KNN. Every body have been proofreading each others texts and re-regulated
%the structure of the report under writing part of the project.
I mainly been involved in work concerning the parsing and interpretation of the 
input string given by the user, hence the $NLP$ and parsing part of the project.
When it comes to the planning part I mostly worked on on the heuristic function.
I have also done code work concerning the setup scripts for the web server,
implementation of error handling in code and the integration between our code
and the server. When it comes to the report writing I mainly written text
concerning the planner and the planer in combination with the parser. 
There have also been a lot of proof-reading. 
\\\\
In addition to what can be seen in the report and the code there have been a lot
of discussions in the group concerning what sentences given by the user actually
means. Since they many times are ambiguous there were some disagreements but
nevertheless this really approved the work. It became clearer what was hard and
were we should focus over work. The advantage here was that the group was able
to handle conflicts which I believe later on benefited the work for
everybody. 
%The project benefited much from the fact that all members of the group have
%already taken a course in machine learning. This means that the concepts of
%machine learning were already clear before the project started. This
%gave rise to that we could focused the work on how we should process the data
%and how we should interpret the results between different algorithms and
%distinguished input.
\\\\
I think the above facts resulted in an interesting project and much fun to be a
part of the group.

%\section{Classifiers}

%\section{Report}
%Formost parts that are written by me in report is.
%\begin{itemize}
%\item Problem description
%\item Representing text
%\item K-Nearest Neighbour (KNN) algorithm
%\item Feature Vector / Text Representation
%\end{itemize}
