\chapter{Introduction}
This project is about machine learning of different statistical classifiers. 
Machine learning is about construct and study systems that can learn from data. 
This could be used to train a system to recognize patterns in, for instance, emails and learn how to distinguish between spam and non-spam messages. In this project the classifiers are applied to reviews and the task is to categorize these. 
By statistical analysis of experiments, the classifiers are compared in terms of, for instance, classification accuracy.

\section{Problem description}
The problem 

Here you describe the problem in your own words!
\\\\
implementera:\\
* naive bayes\\
* perceptron\\
* average perceptron\\
* knn\\
* (svm)
\\\\
testa:\\
* in-domain sentimental\\
* out-domain sentimental\\
* test categorization
\\\\
features:\\
* unigram\\
* bigram\\
* snowball\\
* tf-idf\\
* stopwords

\section{Theory}
Describe briefly the scientific papers or book chapters you found relevant to the problem, references to sec 6. Explain which are relevant for your project and which not and why.
\\\\
hitta kapitel om\\
* naive bayes\\
* perceptron\\
* knn\\
* svm \\
* text categorization

\subsection{The Perceptron}
Perceptron is a linear, supervised classification algorithm. The perceptron algorithm consider a 0/1 classification problem. 
The algorithm tries to separate the input data with a linear decision boundary, as shown in Picture X. The algorithm output a weight vector which should represent the line between the two separated classes for each input data point. 
\\
--bild-- 
\\\\
There is also another variant of the perceptron algorithm, which is called averaged perceptron. They work in the same way, except that the averaged perceptron outputs the averaged weight vector instead of the final one.
\\\\
http://sites.stat.psu.edu/~jiali/course/stat597e/notes2/percept.pdf

\subsection{Programs and tools}
What tools and programs are already available for the problem, or for closely related ones?
Describe these briefly. Say how you can use them, and how your work will build on them, or differ from them. Explain which are relevant for your project and which not and why.
\\\\
* vilka program är vettiga att använda? -leta upp några-fördelar/nackdelar
skriv att vi valde matlab och varför.

